Visualization tool for comparison of a single amino acid change in protein simulation

### 2017-08-02 paper/paper.tex
paper

\subsection{Related work}
%

@@

The data for testing this visualization tool comes from the Kappa-conotoxin PVIIA, with amino acids sequence: $CRIPNQKCFQHLDDCCSRKCNRFNKCV$. Its three dimensional structure, obtained with nuclear magnetic resonance (NMR) from the Protein Data Bank (PDB) under the code 1AV3, can be seen in Fig.~\ref{fig:pviia}. Kappa-conotoxins are neurotoxical proteins extracted from sea slugs poison. They are inhibitors of the potassium channel and when injected in different organisms some alterations in their effect can be observed, from hyperactivity in fish to death when combined with other variants of conotoxins. The substitution of the asparagine ($N$) in the fifth position in the amino acids chain of the Kappa-conotoxin PVIIA by an alanine ($A$) is know to cause a reduction of 100\% in the toxicity of this protein~\cite{jacobsen2000single}~\cite{mir2016conotoxins}~\cite{akey2002inherited}.

@@

\subimages[htb]{Comparison between the simulations with asparagine (yellow) and alanine (red) for at three different moments.}{fig:alaasn}{%
  \subimage[Time step 30000]{.48}{alaasn30000.png}%
  \subimage[Time step 40000]{.48}{alaasn40000.png}% 
  \\
  \subimage[Time step 50000]{.48}{alaasn50000.png}%
}

@@

\subimages[htb]{Comparison between the simulations with asparagine (red), glycine (yellow) and proline (blue) for at three different moments.}{fig:asnglypro}{%
  \subimage[Time step 30000]{.48}{asnglypro30000.png}%
  \subimage[Time step 40000]{.48}{asnglypro40000.png}% 
  \\
  \subimage[Time step 50000]{.48}{asnglypro50000.png}%
}

@@

\subimages[htb]{Comparison between the simulations with asparagine (red), aspartic acid (yellow) and methionine (blue) for at three different moments.}{fig:asnaspmet}{%
  \subimage[Time step 30000]{.48}{asnaspmet30000.png}%
  \subimage[Time step 40000]{.48}{asnaspmet40000.png}% 
  \\
  \subimage[Time step 50000]{.48}{asnaspmet50000.png}%
}

>>>>

\subsection{Related work}
%
The work in~\cite{likhachev2016available} reviews some of the available instruments when analyzing molecular dynamics trajectories, including visualization tools. OVITO~\cite{stukowski2009visualization} is an open visualization tool for atomistic simulation data. TRAVIS~\cite{brehm2012travis} is a free analyzer and visualizer for Monte Carlo and molecular dynamics trajectories. The study in~\cite{garg2010visualization} presents a visualization tool for many tasks of molecular dynamics simulation. QwikMD~\cite{ribeiro2016qwikmd} is a toolkit that includes tools for analyzing simulations.

@@

The data for testing this visualization tool comes from the Kappa-conotoxin PVIIA, with amino acids sequence: $CRIPNQKCFQHLDDCCSRKCNRFNKCV$. Its three dimensional structure, obtained with nuclear magnetic resonance (NMR) from the Protein Data Bank (PDB) under the code 1AV3~\cite{scanlon1997solution}, can be seen in Fig.~\ref{fig:pviia}. Kappa-conotoxins are neurotoxical proteins extracted from sea slugs poison. They are inhibitors of the potassium channel and when injected in different organisms some alterations in their effect can be observed, from hyperactivity in fish to death when combined with other variants of conotoxins. The substitution of the asparagine ($N$) in the fifth position in the amino acids chain of the Kappa-conotoxin PVIIA by an alanine ($A$) is know to cause a reduction of 100\% in the toxicity of this protein~\cite{jacobsen2000single}~\cite{mir2016conotoxins}~\cite{akey2002inherited}.

@@

\subimages[htb]{Comparison between the simulations with asparagine (yellow) and alanine (red) at three different moments.}{fig:alaasn}{%
  \subimage[Time step 30000]{.48}{alaasn30000.png}%
  \subimage[Time step 40000]{.48}{alaasn40000.png}% 
  \\
  \subimage[Time step 50000]{.48}{alaasn50000.png}%
}

@@

\subimages[htb]{Comparison between the simulations with asparagine (red), glycine (yellow) and proline (blue) at three different moments.}{fig:asnglypro}{%
  \subimage[Time step 30000]{.48}{asnglypro30000.png}%
  \subimage[Time step 40000]{.48}{asnglypro40000.png}% 
  \\
  \subimage[Time step 50000]{.48}{asnglypro50000.png}%
}

@@

\subimages[htb]{Comparison between the simulations with asparagine (red), aspartic acid (yellow) and methionine (blue) at three different moments.}{fig:asnaspmet}{%
  \subimage[Time step 30000]{.48}{asnaspmet30000.png}%
  \subimage[Time step 40000]{.48}{asnaspmet40000.png}% 
  \\
  \subimage[Time step 50000]{.48}{asnaspmet50000.png}%
}
